Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-28 cbm-rbd-paper.tex
typo in 5.2., some clarification in 5.3

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on the realization of $\Tsysnow$, the unit cost rate is 
\begin{align*}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau  & \text{if } \tsysnow \ge \tau \\
c_u / \Tsys & \text{if } \tsysnow < \tau
\end{cases}
\end{align*}
Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t
\label{eq:gtau}
\end{align}
Note that for the integral to exist in \eqref{eq:gtau},
$\E[\Tsysnow]$ must exist, which is a condition for $\fsysnow(t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
For our approach, however, this condition is not relevant,
as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively.
We will describe next how this approximation is used in \eqref{eq:gtau}.
%($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.

@@

%*** not possible / *** to minimize $\gnow(\tau)$ analytically.
***we calculate $\Rsysnow(t)$ on discrete grid until some horizon, optimize $\tausnow$ over same discrete grid.

We approximate the integral in \eqref{eq:gtau} numerically by a sum,
where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on a dense grid.
$\gnow(\tau)$ is likewise evaluated on a dense grid,
and $\tau_*^{(\tnow)} = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
%The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
%$\tau^*$ depends on $\tnow$, and also on the history of the system.

@@

***if min $\gnow(\tau)$ at horizon, corrective maintenance is optimal: policy switch!
%***if $\tau_*^{(\tnow)}$ larger than certain horizon, than conclude corrective policy

>>>>

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on the realization of $\Tsysnow$, the unit cost rate is 
\begin{align*}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau  & \text{if } \tsysnow \ge \tau \\
c_u / \Tsys & \text{if } \tsysnow < \tau
\end{cases}
\end{align*}
Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t
\label{eq:gtau}
\end{align}
Note that for the integral to exist in \eqref{eq:gtau},
$\E[1/\Tsysnow]$ must exist, which is a condition for $\fsysnow(t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
For our approach, however, this condition is not relevant,
as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively.
We will describe next how we numerically evaluate \eqref{eq:gtau} and find $\tausnow$.
%($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.

@@

%*** not possible / *** to minimize $\gnow(\tau)$ analytically.
***we calculate $\Rsysnow(t)$ on discrete grid from $\tnow$ until some horizon time $\tnow + t_h$.
$t_h$ can be determined by practical considerations,
but generally should reach into the tail of $\Rsysnow(t)$.
We calculate $\gnow(\tau)$ on the same grid,
and determine $\tausnow$ as the minimum over this grid.

We approximate the integral in \eqref{eq:gtau} numerically by a sum,
where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on a dense grid.
$\gnow(\tau)$ is likewise evaluated on a dense grid,
and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
%The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
%$\tau^*$ depends on $\tnow$, and also on the history of the system.

@@

***if min $\gnow(\tau)$ at $\tnow + t_h$, corrective maintenance is optimal: policy switch!
%***if $\tau_*^{(\tnow)}$ larger than certain horizon, than conclude corrective policy
